Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions

### 2024-01-05 paper/main_sections/6_tail.tex
fix symbol format
adjust empty lines

\subsection{Data Availability}
Essential source data required to replicate the study's results-including VASP input files,
structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.

\subsection{Code Availability}
Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos, or obtained from the corresponding authors upon request.

@@

\subsection{Author Contributions}
H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
J.Z. engaged in valuable discussions on DFT calculations.
Q.W. provided advice on the computer code revisions.
W.L. facilitated resource acquisition and offered research supervision.
B.L. provided guidance on DFT calculations and offered research supervision.
Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.

>>>>

\subsection{Data Availability}
Essential source data required to replicate the study's results-including VASP input files,
structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
at \url{https://github.com/DanielYang59/cnn4dos} or can be provided by the corresponding authors upon request.
Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.

\subsection{Code Availability}
Associated computer code for this study can be accessed on GitHub at \url{https://github.com/DanielYang59/cnn4dos},
or obtained from the corresponding authors upon request.

@@

\subsection{Author Contributions}
H.Y. performed DFT calculations, implemented Python code for machine learning methodologies and data analysis,
and drafted and refined the manuscript.
J.Z. engaged in valuable discussions on DFT calculations.
Q.W. provided advice on the computer code revisions.
W.L. facilitated resource acquisition and offered research supervision.
B.L. provided guidance on DFT calculations and offered research supervision.
Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.
